### 2009-02-26 doc/ws-programming-tutorial/doc/tex_tls_echoservice/tls_echoservice.tex
Enhanced the chapter about the service using TLS

At startup of the communication process A (Alice) who desires a secure connection transmits her public key to B (Bob).
Bob is now able to encrypt the messages such that only A is able to decrypt them.
As one can see this first approach already provides confidentiality and integrity of messages.
%
Non-repudiation, authentication and due to that access control are not given because the identity of Alice is not proven.
In order to be able to check identities so called certificates must be introduced.
Certificates render the possibility to validate the identity of its owner. They are signed by a certificate authority (CA) which's identity can be resolved to another CA or which is  pre-configured to be trusted.
A certificate is composed of its owner's public key, his identity, the name of the signing CA and a signiture which is a hash-value of the certificate encrypted with the private key of the CA. 
If a certificate can be resolved to a CA with is pre-configured to be trusted, the identity of the certificate owner is considered as to be proven. 
In general a set of trusted CAs is already defined in the operation system.
To obtain a certificate a certificate request has to be submitted to a CA.
After the CA has verified the identity of the requesting person and the requested certificate will be signed.
Figure~\ref{fig:certificate_request} shows the procedure of gaining a certificate.
\begin{figure}[htb]
	\centering%epstopdf certificates.eps
 	\includegraphics[width=13cm]{tex_tls_echoservice/certificates.pdf}
	\mycaption{specific}{general}
	\label{fig:certificate_request}
\end{figure}
A private and a public key is generated by the requester and a request containing an unsigned certificate is created. The unsigned certificate is submitted to a CA which validates the authentity. If the CA decides to sign the request, a hash will be created for the request with a negotiated algorithm. (A fixed-sized short string which is generated by an algorithm based on a given text. A small change in the text causes the hash value to change almost like a random function such that the hash value can be used a fingerprint of the text.) Than the certificate will be signed by encrypted the hash value with the private key.
%
%
In case a third person wants to verify the certificate owner, the encrypted hash value have to be

Figure~\ref{fig:verification_of_certificates} shows a usecase where Alice wants to resolve the identity of Bob. Alice submitts her request to Bob along with a challange consisting of a random number $n$. Bob encrypts the number with his private key and returns it together with his certificate. With the usage of the public key, Alice is able to decrypt the challange which implies that, if the certificate is to be trusted, the identity of Bob is to be trusted. Unfortunately Alice is unable to verify the certificate because it is signed by an unknown CA called CA 1. She establishes the connection to CA 1 in order to resolve the identity of that certificate authority. Again Alice sends a challenge --- this time to the certificate authority CA 1. CA 1 encrypts the challange with its private key and submits the result along with its certificate. Again Alice validates the certificate sucessfully. 
The certificate was signed by a CA called CA 2 which she is able to locate as a pre-configured certificate. Due to the reason she trusts CA 2, she can trust CA 1 and finally Bob.

\begin{figure}[htb]
	\centering%epstopdf verification.eps 
	\includegraphics[width=13cm]{tex_tls_echoservice/verification.pdf}
	\mycaption{specific}{general}
	\label{fig:verification_of_certificates}
\end{figure}

The advantages of certificates are
o easy scalable to a larger set of users
o VOMs are realisable
o Infrastructure is given and easily to maintain
o In general the pre-configured organistion take money to sign certifcates, but they can also be created locally.

@@

o What do we need to get a service running
clientCA   - Authority guarantee for identity
clientCERT - Certificate given
clientKEY  - Secret key of the client to read messages, encrypted by the public key in the certificate!

@@

>>>>

At startup of the communication process A (Alice) who desires a secure connection transmits her public key to B (Bob).
Bob is now able to encrypt the messages such that only A is able to decrypt them.
As one can see this first approach already provides confidentiality and integrity of messages.
%
Non-repudiation, authentication and due to that access control are not given because the identity of Alice is not proven.
In order to be able to check identities so called certificates must be introduced.
Certificates render the possibility to validate the identity of its owner. They are signed by a certificate authority (CA) which's identity can be resolved to another CA or which is  pre-configured to be trusted.
A certificate is composed of its owner's public key, his identity, the name of the signing CA and a signiture which is a hash-value of the certificate encrypted with the private key of the CA. 
If a certificate can be resolved to a CA with is pre-configured to be trusted, the identity of the certificate owner is considered as to be proven. 
In general a set of trusted CAs is already defined in the operation system.
To obtain a certificate a certificate request has to be submitted to a CA.
After the CA has verified the identity of the requesting person and the requested certificate will be signed.
Figure~\ref{fig:certificate_request} shows the procedure of gaining a certificate.
\begin{figure}[htb]
	\centering%epstopdf certificates.eps
 	\includegraphics[width=13cm]{tex_tls_echoservice/certificates.pdf}
	\mycaption{specific}{general}
	\label{fig:certificate_request}
\end{figure}
In the first step, a private and a public key will be generated by the requester. The public key together with a textual description of the identity  depict the request which will be transmitted to a CA. After the CA successfully varified the validity of the request, the identity of the CA and the name of used the encryption algorithms are added.
The collected data will represent the plain text of the certificate. In order to ensure the integrity of the text, 
a hash value will be created. (A fixed-sized short string which is generated by an algorithm based on an arbitrary long given text. The algorithm is designed such that a small change in the text will cause the hash value to change almost like a random function. Thus, the hash value can be used a fingerprint of the text.) The CA signs the plain certificate by encrypting its hash value with its private key. Finally the signed certifcate will be returned to the requester.
%
%
If an outside person wants to verify the certificate owner, the encrypted hash value has to be decrypted by the public key of the CA and a hash value has to be created with the same algorithm in order to compare them.\\

Figure~\ref{fig:verification_of_certificates} shows a usecase in which Alice wants to resolve the identity of Bob. Alice submitts her request to Bob along with a challange consisting of a random number $n$. 
The random number ensures that it is not possible to repeat a message (integrity).
Bob encrypts the number with his private key and returns it together with his certificate. Alice uses the public key of Bob to decrypt the challange. 
If the decrypted number is equal to the transmitted number, Alice can reason that the identity of Bob is to be trusted in case she is trusting the CA which has signed Bobs certificate. 
%
In the given example Alice only trusts the CA 2 but not CA 1.
In order to resolve the identity, Alice establishes a connection to CA 1 and submits another random number $n$ as a challenge.
The CA 1 encrypts the challange with its private key and send the result along with its certificate back to Alice. Alice succefully validates the certificate of CA 1. Due to the certificate was signed by CA 2 which is pre-configured to be trusted she can follow to trust CA 1 and in conclusion the identity of B. In summary, Alice knows she is talking to Bob. If Bob also wants to be sure how he's talking to the same procedure has to be done for the identity of Alice. The TLS mode in in which both endpoints are ensuring themself to whom they are talking to is called bilateral connection.
Due to the client is aware of the service authentity, the confidential treatment of his data is given such that it won't be revealed to a third party (service sided confidentiality). Moreover the access to the service can be controled (access control) and the results are only passed back to the right person (client sided confidentiality). 
As one can see confidentiality, authentication, integrity and non-repudiation are now given.\\
\begin{figure}[htb]
	\centering%epstopdf verification.eps 
	\includegraphics[width=13cm]{tex_tls_echoservice/verification.pdf}
	\mycaption{specific}{general}
	\label{fig:verification_of_certificates}
\end{figure}

Certificates have several advantages. They are scaling very good with the amount of users because CAs can create new sub-CAs such that the load is balanced (certificates of a CA may be cached). Furthermore no critical information is exchanged which may gets intercepted - in particular no secret key is shared. Instead a set of pre-configured CAs which will be in general provided by the operation system is needed.
In respect of ARC it is obvious, that the access to the grid should be under control of its administrator. To do so, the administrator have to build up his own CA to be in charge of creating certificates for a set of users. 
The created CA have to be shipped into the directory of pre-configured CAs.
(Within the source code there are two shell scripts to create a CA and related certificates). Due to there's a bunch of tools for certificates (like \textit{openssl}) it is easy to maintain them.

o Infrastructure is given and easily to maintain

o In general the pre-configured organistion take money to sign certifcates, but they can also be created locally.

o VOMs are realisable

ARC:

@@

o What do we need to get a service running

clientCA   - Authority guarantee for identity
clientCERT - Certificate given
clientKEY  - Secret key of the client to read messages, encrypted by the public key in the certificate!

@@

\task{RENAMING into~ARC service configuration file}
\task{echo service client configuration file}
